Individual and Differential Harm in Redistricting

### 2022-06-17 paper/paper.Rmd
acknowledgements

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed.
      The authors thank participants of the Harvard American Politics
      Research Workshop and Imai Research Group  for helpful comments and discussion.
      Replication code and data are available at <https://github.com/CoryMcCartan/harm-redistricting>.
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Social scientists have developed dozens of measures for assessing partisan bias in redistricting. But these measures cannot be easily adapted to other groups, including those defined by race, class, or geography. Nor are they applicable to single- or no-party contexts such as local redistricting. To overcome these limitations, we propose a unified framework of harm for evaluating the impacts of a districting plan on individual voters and the groups to which they belong. We consider a voter harmed if their chosen candidate is not elected under the current plan, but would be under a different plan. Harm improves on existing measures by both focusing on the choices of individual voters and directly incorporating counterfactual plans. We discuss strategies for estimating harm, and demonstrate the utility of our framework through analyses of partisan gerrymandering in New Jersey, voting rights litigation in Alabama, and racial dynamics of Boston City Council elections.
keywords:
  - representation
  - redistricting
  - voting rights
  - individual harm
bibliography: references.bib
biblio-style: chicago
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options:
  markdown:
    wrap: sentence
---

>>>>

---
title: Individual and Differential Harm in Redistricting
authors:
  - name: Cory McCartan
    thanks: |
      To whom correspondence should be addressed.
      The authors thank Kosuke Imai, Gary King, Shiro Kuriwaki, 
      Tyler Simko, Nicholas Stephanopolous, and 
      participants of the Harvard American Politics Research Workshop 
      and Imai Research Group for helpful comments and discussion.
      Replication code and data are available at <https://github.com/CoryMcCartan/harm-redistricting>.
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Social scientists have developed dozens of measures for assessing partisan bias in redistricting. But these measures cannot be easily adapted to other groups, including those defined by race, class, or geography. Nor are they applicable to single- or no-party contexts such as local redistricting. To overcome these limitations, we propose a unified framework of harm for evaluating the impacts of a districting plan on individual voters and the groups to which they belong. We consider a voter harmed if their chosen candidate is not elected under the current plan, but would be under a different plan. Harm improves on existing measures by both focusing on the choices of individual voters and directly incorporating counterfactual plans. We discuss strategies for estimating harm, and demonstrate the utility of our framework through analyses of partisan gerrymandering in New Jersey, voting rights litigation in Alabama, and racial dynamics of Boston City Council elections.
keywords:
  - representation
  - redistricting
  - voting rights
  - individual harm
bibliography: references.bib
biblio-style: chicago
output:
  rticles::arxiv_article:
    keep_tex: true
    includes:
      in_header: "header.tex"
    latex_engine: pdflatex
editor_options:
  markdown:
    wrap: sentence
---
